---
title: "ANSI CSI SGR in Rmarkdown"
author: "Brodie Gaslam"
output:
    rmarkdown::html_vignette:
        css: styles.css
mathjax: local
vignette: >
  %\VignetteIndexEntry{ANSI CSI SGR in Rmarkdown}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r echo=FALSE}
library(fansi)
```

Over the past few years color has been gaining traction in the R terminal.
Gábor Csárdi's [crayon](https://github.com/r-lib/crayon) made it easy to format
text with [ANSI CSI SGR sequences](https://en.wikipedia.org/wiki/ANSI_escape_code).  Unfortunately these sequences are not
recognized by web browsers, and instead end up rendering weirdly:

```{r}
sgr.string <- c(
  "\033[43;34mday > night\033[0m",
  "\033[44;33mdawn < dusk\033[0m"
)
writeLines(sgr.string)
```

`fansi` provides the `sgr_to_html` function which converts the ANSI CSI SGR
sequences into HTML markup.  When we combine it with `knitr::knit_hooks` we can
modify the rendering of the `rmarkdown` document such that ANSI CSI SGR
encoding is shown in the equivalent HTML.

`fansi::set_knit_hooks` is a convenience function that does just this.  You
should call it in an `rmarkdown` document with the:

  * Chunk option `results` set to "asis".
  * Chunk option `comments` set to "".
  * The `knitr::knit_hooks` object as an argument.

The corresponding `rmarkdown` hunk should look as follows:

    ```{r comment="", results="asis"}
    old.hooks <- fansi::set_knit_hooks(knitr::knit_hooks)
    ```

```{r comment="", results="asis", echo=FALSE}
old.hooks <- fansi::set_knit_hooks(knitr::knit_hooks)
```
We run this function for its side effects, which cause the output to be
displayed as intended:

```{r}
writeLines(sgr.string)
```

We can also set hooks for the other types of outputs, and add some additional
CSS styles.

    ```{r comment="", results="asis"}
    styles <- c(
      getOption("fansi.style"),  # default style
      "PRE.fansi CODE {background-color: transparent;}",
      "PRE.fansi-error {background-color: #DDAAAA;}",
      "PRE.fansi-warning {background-color: #DDDDAA;}",
      "PRE.fansi-message {background-color: #AAAADD;}"
    )
    old.hooks <- c(
      old.hooks,
      fansi::set_knit_hooks(
        knitr::knit_hooks,
        which=c("warning", "error", "message"),
        style=styles
    ) )
    ```
```{r comment="", results="asis", echo=FALSE}
styles <- c(
  getOption("fansi.style"),  # default style
  "PRE.fansi CODE {background-color: transparent;}",
  "PRE.fansi-error {background-color: #DDAAAA;}",
  "PRE.fansi-warning {background-color: #DDDDAA;}",
  "PRE.fansi-message {background-color: #AAAADD;}"
)
old.hooks <- c(
  old.hooks,
  fansi::set_knit_hooks(
    knitr::knit_hooks,
    which=c("warning", "error", "message"),
    style=styles
) )
```
```{r error=TRUE}
message(paste0(sgr.string, collapse="\n"))
warning(paste0(c("", sgr.string), collapse="\n"))
stop(paste0(c("", sgr.string), collapse="\n"))
```

You can restore the old hooks at any time in your document with:

```{r}
do.call(knitr::knit_hooks$set, old.hooks)
writeLines(sgr.string)
```

See `?fansi::set_knit_hooks` for details.

**A note on `crayon`**: if you use `crayon` to generate your ANSI CSI SGR style
strings you may need to set `options(crayon.enabled=TRUE)`, as in some cases
`crayon` suppresses the SGR markup if it think it is not outputting to a
terminal.

